Data_extractions

### 2019-02-06 Data_extractions.Rmd
typo fixed

You will need to open the pdf files and take the snapshots of the relevant figures (for MacOS the keyboard shortcut is easiest: press Command+Shift+4 and then select the screen fragment; for Windows see https://www.windowscentral.com/how-take-windows-10-screenshot-7-best-techniques). Make sure you capture the axes and axes labels. Also, enlarge these figures to fill the screen before taking the snapshot to get a higher resolution image.

@@

Its good to enter sample sizes at this point. Since there is no such info in the plot or under the plot, search the full text for the sample sizes (hint: look in "Statistical anlaysis"). Ideally, to do it efficiently you would already have extracted this and other available information into your spreadsheet, then saved the figures, and then come back at the end to process all the figures at once. This way you have everything at hand when you do data extraction from the figures.

@@

Now you should be able to extractdata from **plot 002_Sadd_2006_Fig2a.png**! (hint: extract "treatment control" and "treatment" groups).

@@

In practice, we would preer to do this in R, rather than in an online app or any other non-scriptable software that cannot socument our calculations. Luckily, the R package *compute.es* allows us to not only compute various effect sizes from descriptive statistics, but also from inferential statistics.

>>>>

You will need to open the pdf files and take the snapshots of the relevant figures (for Mac OS the keyboard shortcut is easiest: press Command+Shift+4 and then select the screen fragment; for Windows see https://www.windowscentral.com/how-take-windows-10-screenshot-7-best-techniques). Make sure you capture the axes and axes labels. Also, enlarge these figures to fill the screen before taking the snapshot to get a higher resolution image.

@@

Its good to enter sample sizes at this point. Since there is no such info in the plot or under the plot, search the full text for the sample sizes (hint: look in "Statistical analysis"). Ideally, to do it efficiently you would already have extracted this and other available information into your spreadsheet, then saved the figures, and then come back at the end to process all the figures at once. This way you have everything at hand when you do data extraction from the figures.

@@

Now you should be able to extract data from **plot 002_Sadd_2006_Fig2a.png**! (hint: extract "treatment control" and "treatment" groups).

@@

In practice, we would prefer to do this in R, rather than in an online app or any other non-scriptable software that cannot document our calculations. Luckily, the R package *compute.es* allows us to not only compute various effect sizes from descriptive statistics, but also from inferential statistics.
